Missing The Point

### 2020-10-20 Manuscript.Rmd
Add even more iterations to case study and interpret

- We compare non-convergence identified using visual inspection versus rhat in the chain variances, scientific estimate and lambda

@@

```{r echo=FALSE}
# p <- casestudy_plot(v="est", name = "Regression estimate")
# p # %>% plotly::ggplotly()
```

@@

@@

@@

>>>>

- We compare non-convergence identified using visual inspection versus rhat in the chain variances, scientific estimate and lambda.

- The figures show results of a `mice` run with 30 iterations but otherwise default settings.

@@

```{r echo=FALSE}
# p <- casestudy_plot(v="est", name = "Regression estimate")
# p %>% plotly::ggplotly()
```

@@

This figure shows that 36 iterations are required before the $\widehat{R}$-values of the chain means drop below the threshold for non-convergence.

@@

The scientific estimate reaches the threshold much sooner, when $it=15$.

@@

According to the $\widehat{R}$-values of the novel parameter, at least 25 iterations are required.

[Is this a nice example? Why is convergence so slow? Don't the defaults work? Is this the bmi+wgt+wgt problem? Maybe find an easier problem?]
